What is disputed on the web?

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Tweaked related work to talk about contradiction detection before dispute finding

In our research, we are following a third approach. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed by another source. For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder knows about another page that argues that this claim is false, then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''. 
But a contradicted claim is not necessarily a disputed claim. In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine whether this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. Kawahara et al~\cite{Kawahara2008} and Statement Map~\cite{Murakami2009} use contradiction detection to inform a user when a set of documents contain claims that appear to contradict each other. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine. 
The corresponding disadvantage would be that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.

Perhaps more importantly, for our purposes disputes are more interesting than contradictions. We are interested in the social side of dispute. We want to know who disagrees with who, why they disagree, and what they think is important.

>>>>

A third approach is to inform a user when a document contains information that other sources disagree with. Annotation tools such as ReframeIt.com, ShiftSpace.org, and SpinSpotter.com allow a user to manually annotate a web page that they disagree with, overlaying their own opinions on top of existing content. 
Cohere~\cite{Shum2008} allows a user to manually annotate a web page as making a claim that is part of an argumentation graph. These tools work well when a user has marked up the page the user is reading, but are limited by the requirement that a human needs to manually mark up each page.

In previous work, we have build an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs a user when a web page that they are reading makes a claim that it knows to be disputed by another source. For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder recognizes this as being an instance of a known disputed claim, then Dispute Finder will highlight the text as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to its corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com). This approach scales better than having users manually mark individual pages, but it is still difficult to make this approach scale to the huge number of claims on the web that are disputed.

A more scalable approach is to automatically detect when web pages disagree with each other. Tools like Statement Map~\cite{Murakami2009} and WISDOM~\cite{Kawahara2008} use {\it contradiction detection} to inform a user when one document contains a statement that contradicts a statement on another web page.

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine whether this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

In our work, we attempt to bypass the difficulty of contradiction detection by looking for {\it disputes} rather than {\it contradictions}. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. 
Looking for disputes rather than contradictions allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that tells us that the author believes that other web pages are claiming that ``Obama is a Muslim'' and that the author believes this claim is false. For our purposes, disputes are also more interesting than contradictions. We are interested in the social side of dispute. We want to know who disagrees with who, why they disagree, and what they think is important.

One disadvantage of looking for disputed claims rather than contradictions is that it limits us to only finding those claims that some human has explicitly said they disagree with. For a small corpus this would be a limiting factor; however our hypothesis is that the web is sufficiently large that, at least for areas of general interest, any sufficiently important claim that is false will be explicitly disputed by somebody.

@@
